---
title: "San Jose City Council Members"
date: 2016-04-05
tags: [San Jose, city council]
categories: [Research]
project: machinesvalley
---

Name                            Date Elected        Date Left
-------------------------       ------------        ---------
Clyde L. Fischer                1936                1946
Fred Watson                     1944                1961
Parker L. Hathaway              1948                1965
George Starbird                 1950                1962
Louis S. Solari                 1952                1969
Paul Moore                      1954                1962
Robert C. Doerr                 1956                1965
Emery J. Delmas                 1956                1960
Robert J. Welch                 1960                1968
George Siegfried                1961                1962
Virginia C. Schaffer            1962                1971
Clyde L. Fischer                1962                1967
Joseph L. Pace                  1962                1967
Robert J. Miller                1965                1969
Ronald R. James                 1965                1971
Joseph A. Colla                 1967                1978
Norman C. Mineta                1967                1971
John F. Lisher                  1968                1969
Clyde L. Fischer                1969                1969
Kurt Gross                      1969                1971
Walter V. Hays                  1969                1973
David J. Goglio                 1969                1973
Janet Gray Hayes                1971                1974
Roy B. Naylor                   1971                1976
Alfredo Garza                   1971                1980
Susanne B. Wilson               1973                1978
James Self                      1973                1980
Lawrence R. Pegram              1975                1980
David Runyon                    1977                1978
Thomas McEnery                  1978                1980
Jerry T. Estruth                1979                1980
Iola M. Williams                1979                1980
Susan Hammer                    1980                1980
Robert E. Perez                 1980                1980
Lu Ryden                        1981                1982
Lu Ryden                        1983                1986
Lu Ryden                        1987                1990
Blanca Alvarado                 1981                1982
Blanca Alvarado                 1983                1986
Blanca Alvarado                 1987                1990
Blanca Alvarado                 1991                1994
James Beall Jr.                 1981                1982
James Beall Jr.                 1983                1986 
James Beall Jr.                 1987                1990
James Beall Jr.                 1991                1994
Shirley Lewis                   1981                1984
Shirley Lewis                   1985                1988
Shirley Lewis                   1989                1992
Nancy Ianni                     1981                1984
Nancy Ianni                     1985                1988
Nancy Ianni                     1989                1992
Patricia E. Sausedo             1981                1984
Patricia E. Sausedo             1985                1988
Patricia E. Sausedo             1989                1992
Claude C. Fletcher              1981                1984
Susan Hammer                    1983                1986
Susan Hammer                    1987                1990
Judy Stabile                    1985                1988
Judy Stabile                    1987                1990
Bob Putnam                      1985                1988
Joe Head                        1989                1992
Joe Head                        1993                1996
Trixie Johnson                  1991                1994
Trixie Johnson                  1995                1998
David Pandori                   1991                1994
David Pandori                   1995                1998
George Shirakawa                1991                1994
Charlotte Powers                1993                1996
Charlotte Powers                1997                2000
Margie Fernandes                1993                1996
Margie Fernandes                1997                2000
Frank Fiscalini                 1993                1996
Frank Fiscalini                 1997                2000
Kathryn Cole                    1993                1996
Alice E. Woody                  1994                1996
Alice E. Woody                  1997                2000
George Shirakawa Jr.            1994                1994
George Shirakawa Jr.            1995                1998
George Shirakawa Jr.            1999                2002
Manny Diaz                      1995                1998
Manny Diaz                      1999                2002
John Diquisto                   1995                1998
John Diquisto                   1999                2002
Pat Dando                       1995                1996
Pat Dando                       1997                2000
Pat Dando                       2001                2004
Linda J. LeZotte                1999                2002
Linda J. LeZotte                2003                2006
Cindy Chavez                    1999                2002
Cindy Chavez                    2003                2006
Forrest Williams                2001                2004
Forrest Williams                2005                2008
Chuck Reed                      2001                2004
Chuck Reed                      2005                2006
Chuck Reed                      2007                2010
Chuck Reed                      2011                2014
Ken Yeager                      2001                2004
Ken Yeager                      2005                2006
David Cortese                   2001                2004
David Cortese                   2005                2008

```{r}
library(googlesheets)
library(tidyverse)
library(ggrepel)
library(ggalt)
library(jahMisc)

data <- gs_title("San Jose City Council")
data_sj <- gs_read(ss = data, ws = "Sheet1")

data_transform <- data_sj %>% 
  mutate(year_elected_jitter = jitter(year_elected)) %>% 
  mutate(year_left_jitter = year_left + year_elected_jitter - year_elected + 0.01)

# This isn't quite right. Each person needs to be a line segment, not just each year (which is what's happening now)
ggplot(data_transform, aes(year_elected, years_in_office, label = name)) +
  geom_segment(aes(x = year_elected_jitter, y = 0, xend = year_left_jitter, yend = years_in_office, color = gender), size = 0.3) +
  #geom_text_repel(aes(year_left_jitter, label = name)) +
  theme_minimal()
```

A different, and better, timeline view:

```{r}
ggplot(data_sj, aes(y = reorder(name, year_elected), x = year_elected, xend = year_left, color = gender)) + 
  geom_dumbbell(size = 1, dot_guide = TRUE, dot_guide_size = 0.25) +
  theme_minimal() +
  theme(panel.grid.major.x = element_line(size=0.05)) +
  theme(panel.grid.major.y = element_blank()) +
  theme(axis.title.y = element_blank()) +
  xlab("Time in office") +
  theme_roboto()

```